The pollination trade-off

### 2018-08-31 paper/supp-info.Rmd
Do not show table comparing wether community makes a difference
On the gain of conspecific pollen transfer

```{r table-variation-across-sites, results='asis'}
drake::loadd(consp_self)
consp_self %>%
  anova(test = "Chisq")  %>%
  knitr::kable(
    caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).  Density were modelled using a quasipoisson distribution. The model suggests that self-pollination rates are species dependent but not across.',
    booktabs = TRUE) %>%
  kableExtra::kable_styling(font_size = 8)
```

>>>>

```{r table-variation-across-sites, eval=FALSE, results='asis'}
drake::loadd(consp_self)
consp_self %>%
  anova(test = "Chisq")  %>%
  knitr::kable(
    caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).  Density were modelled using a quasipoisson distribution. The model suggests that self-pollination rates are species dependent but not across.',
    booktabs = TRUE) %>%
  kableExtra::kable_styling(font_size = 8)
```
